---
title: "RT-qPCR analysis sample"
author: "Atsushi Hara"
data: 2021年5月28日
output: pdf_document
---

# ライブラリーを読み込む
```{r message=FALSE}
library(tidyverse)
library(ggsignif)
```

# サンプル情報を入力
## 1として調整するサンプル番号(standard), サンプルの群情報(group)を設定
```{r}
standard=1
group=factor(c(0,0,1,0,0,1,1,1,0,0,1,0,1,0),levels=c(0,1))
levels(group) <- c("WT","KO")
```

# サンプルを読み込む
## 最初の７行はいらないので飛ばす
```{r message=FALSE}
tb <- read_csv("sample2.csv", skip=7)
tb
```

```{r message=FALSE}
tb2 <- tb %>%
  select(2,3,10) %>% 
  drop_na()

colnames(tb2) <- c("sample","target","Ct")

tb2 <- tb2 %>% 
  mutate(sample=parse_number(sample)) %>% 
  mutate(expression=2**(-Ct)) %>% 
  select(-Ct) %>% 
  group_by(sample,target) %>% 
  summarize(expression=mean(expression)) %>% 
  ungroup()
tb2
```

```{r message=FALSE}
tb3 <- tb2 %>% 
  arrange(target,sample) %>% 
  pivot_wider(names_from = target, values_from=expression) %>% 
  mutate(group=group)
tb3
```


```{r message=FALSE}
expression <- tb3 %>% 
  select(!c(sample,gapdh,group)) %>% 
  mutate_all(function(x){return(x/tb3$gapdh)})
expression2 <- cbind(tb3 %>% select(sample,group),expression)
expression2
```


```{r message=FALSE}
expression3 <- expression2 %>% 
  mutate_at(-c(1,2),function(x){return(x/x[standard])})
expression3
```

```{r message=FALSE}
expression4 <- expression3 %>% 
  pivot_longer(!c(sample,group),names_to="target",values_to="expression")
expression4
```


```{r message=FALSE}
ggplot(data=expression4) +
  facet_wrap(.~target,ncol=5) +
  geom_bar(aes(x=sample,y=expression),stat="identity")
```
```{r message=FALSE}
expression.summary <- expression4 %>% group_by(target,group) %>% summarize(mean=mean(expression),sd=sd(expression),se=sd(expression)/sqrt(length(expression)),max=max(expression),min=min(expression))
expression.summary
```
```{r message=FALSE}
ggplot(expression.summary) +
  facet_wrap(.~target,ncol=5) +
  geom_bar(aes(x=group,y=mean),stat="identity")
```
```{r message=FALSE}
ggplot(expression.summary) +
  facet_wrap(.~target,ncol=5) +
  geom_bar(aes(x=group,y=mean),stat="identity",fill="grey") +
  geom_errorbar(aes(x=group,ymin=mean-se,ymax=mean+se),width=0.2)
```
```{r message=FALSE}
ggplot(expression4) +
  facet_wrap(.~target,ncol=5) +
  geom_bar(data=expression.summary,aes(x=group,y=mean),stat="identity",fill="grey") +
  geom_signif(aes(x=group,y=expression), comparisons=list(c("WT","KO")), map_signif_level = FALSE, textsize=4, y_position=max(expression.summary$mean)*1.1) + 
  coord_cartesian(ylim=c(0,max(expression.summary$mean)*1.4))
```
```{r message=FALSE}
ggplot(expression4,aes(x=group,y=expression)) +
  facet_wrap(.~target,ncol=5) +
  geom_boxplot(outlier.shape = NA) +
  geom_signif(comparisons=list(c("WT","KO")), map_signif_level = FALSE,textsize=4,y_position=max(expression4$expression)*1.1) + 
  geom_jitter(size = 0.5) +
  coord_cartesian(ylim=c(0,max(expression4$expression)*1.2)) 
```

```{r message=FALSE}
test <- expression4 %>% 
  select(-sample) %>% 
  pivot_wider(names_from = group,values_from = expression,values_fn=list) %>% 
  ungroup %>% 
  group_by(target) %>% 
  mutate(ttest=t.test(unlist(WT),unlist(KO))$p.value) %>% 
  summarize(WT.max=max(unlist(WT)),KO.max=max(unlist(KO)),WT.mean=mean(unlist(WT)),KO.mean=mean(unlist(KO)),ttest=ttest) %>% 
  group_by(target) %>% 
  mutate(max.max=max(WT.max,KO.max),max.mean=max(WT.mean,KO.mean), ttest=round(ttest,digits=2))
test
```
```{r message=FALSE}
ggplot(expression4,aes(x=group,y=expression)) +
  facet_wrap(.~target,ncol=5) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(size = 0.5) +
  geom_segment(data=test,aes(x="WT",xend="KO",y=max.max*1.2,yend=max.max*1.2)) +
  geom_segment(data=test,aes(x="WT",xend="WT",y=WT.max*1.1,yend=max.max*1.2)) +
  geom_segment(data=test,aes(x="KO",xend="KO",y=KO.max*1.1,yend=max.max*1.2)) +
  coord_cartesian(ylim=c(0,max(expression4$expression)*1.3)) +
  geom_text(data=test, aes(x=1.5,y=max.max*1.2+1,label=ttest))
```
```{r message=FALSE}
ggplot(expression4) +
  facet_wrap(.~target,ncol=5) +
  geom_bar(data=expression.summary,aes(x=group,y=mean),stat="identity",fill="grey") +
  geom_segment(data=test,aes(x="WT",xend="KO",y=max.mean*1.2,yend=max.mean*1.2)) +
  geom_segment(data=test,aes(x="WT",xend="WT",y=WT.mean*1.1,yend=max.mean*1.2)) +
  geom_segment(data=test,aes(x="KO",xend="KO",y=KO.mean*1.1,yend=max.mean*1.2)) +
  coord_cartesian(ylim=c(0,max(expression.summary$mean)*1.3)) +
  geom_text(data=test, aes(x=1.5,y=max.mean*1.2+0.25,label=ttest))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
